---
title: Neighbours shapes pollination network topology
output:
    rmdformats::readthedown:
      collapsed: false
      highlight: kate
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(bipartite)
library(igraph)
library(vegan)
library(rnetcarto)
library(corrplot)
library(performance)
```

The front page of the repository containing data and additional code can be accessed here: [https://github.com/jennabraun/foundation-pollination]

### Build network from visitation dataset

```{r, loading clean datasets}
#dataset with aggregated visits (i.e. number of visits per rep, no pollinator ID) with joined covariates & calculated densities
#contains reps with zero visits
#wrangling all done using visits.R

data <- read.csv("Data/Output/visitation_cleaned.csv")

sum(data$Quantity)
#long version with pollinator ID, list of visits only for building network 
visits <- read.csv("Data/visitation_data.csv")
visits$Quantity <- as.numeric(as.character(visits$Quantity))
#some non-pollinator interactions were also recorded but designated with quantity = 0
visits <- dplyr::filter(visits, Quantity>0)
visits$Site <- "site"
visits$ID <- gsub(" ","", visits$ID)
visits$ID <- gsub('\"',"", visits$ID)
visits$Species <- gsub(" ","", visits$Species)
visits$Species <- gsub('\"',"", visits$Species)
sum(visits$Quantity)
visits$uniID <- paste(visits$Species, visits$WP)
```

# Functions
```{r, functions}

#this function creates an adjencancy matrix from the long visit only dataset
#uniID - plant ID, can use to create species/individual/RTU/functional groups networks from dataset
#y is bottom - uniID or plant Species
#z is top - pollinator RTU or functional group
net <- function(x, y, z){
  y <- enquo(y)
  z <- enquo(z)
  fnet <- dplyr::select(x, !!y, !!z, Site, Quantity)
  fnet$Quantity <- as.numeric(fnet$Quantity)
  print(sum(fnet$Quantity))
  long.ag <- fnet %>% group_by(!!y, !!z) %>% summarise(Quantity = sum(Quantity)) 
  print(sum(long.ag$Quantity))
  wide <- spread(long.ag, !!z, Quantity)
  wide[is.na(wide)] <- 0
  wide <- as.data.frame(wide)
  rownames(wide) = wide[,1 ] # the first row will be the header
  rownames(wide) <- wide[,1]
  wide <- select(wide, -!!y)
}

#calculates z-scores
net.zscore = function(obsval, nullval) {
  (obsval - mean(nullval))/sd(nullval)  
}

#creates random network using vegan with fixed marginal totals. Creates 1000 and puts in one big dataframe
ranindices <- function(x, index){
  y <- permatfull(x, fixedmar = "both", times = 1000)
  y <- y$perm
  y_indices <- map(y, networklevel,index = index)
  ran <-  do.call("rbind", y_indices)
  ran <- as.data.frame(ran)
}




#calculates the modularity of 1000 random networks with fixed marginal totals of input and puts in a big dataframe. Bipartite modularity 
ranModules <- function(x){
  y <- permatfull(x, fixedmar = "both", times = 1000)
  y <- y$perm
  z <- list()
  null.mod <- map(y, computeModules)
  for (i in 1:1000){
    ind <- null.mod[[i]]@likelihood
    z <- c(z, ind)
  } 
  do.call(rbind, lapply(z, as.data.frame))
}


```
#  Calculations

## Centrality measures
```{r}
#make an individual network using functional groups
#ind1 <- net(visits, uniID, fun.grp)

ind1 <- net(visits, uniID, ID)

sum(ind1)
#project into a unipartite network
one1 <- as.one.mode(ind1, fill = 0, project = "lower", weight = "TRUE")

#calculate centrality measures
one1 <- graph_from_adjacency_matrix(one1)
cls1 <- closeness(one1)
ei1 <- eigen_centrality(one1)
bt1 <- betweenness(one1)
dg1 <- degree(one1)

#cbind and join to main covariate dataset
dat1 <- as.data.frame(cbind(cls1, ei1$vector, bt1, dg1))
dat1$uniID <- row.names(dat1)
all <- left_join(dat1, data, by = "uniID")

#betweenness is zero inflated so a binary variable
all <- mutate(all, btbin = ifelse(bt1 == 0, 0, 1))

#filter out the over zero part to model separately
bt <- filter(all, bt1 > 0)
```

## Effective partners
```{r, specieslevel indices}
#calculate species level indices
sp <- specieslevel(ind1, index = "effective partners")
pl <- sp[2]
pl <- as.data.frame(pl)
pl$uniID <- row.names(pl)
all <- left_join(pl, all, by = "uniID")
```

## Proportion of conspecific/heterospecific interactors

```{r, population proportions}

#unweighted network
un <- as.one.mode(ind1, fill = 0, project = "lower", weight = "FALSE")

#need to subset
un <- as.data.frame(un)
un$uniID <- row.names(un)
dat <- left_join(all, un, by = "uniID") 
dat <- select(dat, -(18:28))
#calculate number of conspecific interactors
dat <- mutate(dat, cons = ifelse(Species == "PP", rowSums(select (dat, starts_with("PP"))), +
  ifelse(Species == "SC", rowSums(select(dat, starts_with("SC"))),+    ifelse(Species == "HH", rowSums(select(dat, starts_with("HH"))),  +      ifelse(Species == "LT",rowSums(select(dat, starts_with("LT"))), +       ifelse(Species == "AS", rowSums(select(dat, starts_with("AS"))), +      ifelse(Species == "EC", rowSums(select(dat, starts_with("EC"))), +      ifelse(Species == "BW", rowSums(select(dat, starts_with("BW"))), +        ifelse(Species == "EL", rowSums(select(dat, starts_with("EL"))), +  ifelse(Species == "SM", rowSums(select(dat, starts_with("SM"))),
  + ifelse(Species == "SD", rowSums(select(dat, starts_with("SD"))), 0)))))))))))

```

```{r}
#calculate heterospecific interactors

dat <- mutate(dat, hets = ifelse(Species == "PP", rowSums(select(dat, 37:188, 207:265)), +
   ifelse(Species == "SC", rowSums(select(dat, 256:265, 37:206)),+    
 ifelse(Species == "HH", rowSums(select(dat, 37:131, 136:265)),  +      ifelse(Species == "LT",rowSums(select(dat, 37:135, 189:265)), +       ifelse(Species == "AS", rowSums(select(dat, 78:265)), +          ifelse(Species == "EC", rowSums(select(dat, 37:96, 131:265)), +      ifelse(Species == "BW", rowSums(select(dat, 37:77, 96:265)), +        ifelse(Species == "EL", rowSums(select(dat, 37:130, 132:265)), +  ifelse(Species == "SM", rowSums(select(dat, 37:261)),
 + ifelse(Species == "SD", rowSums(select(dat, 37:255, 262:265)), 0)))))))))))


#standardize by abundances
dat <- select(dat, -(37:265))
abun <- dat %>% group_by(Species) %>% count()
dat <- left_join(dat, abun, by = "Species")
dat <- mutate(dat, hetn = 231 - n)
dat <- mutate(dat, st.con = cons/n)
dat <- mutate(dat, st.het = hets/hetn)
dat <- select(dat, uniID, 37:42)
all <- left_join(all, dat, by = "uniID")
```

## Contribution to nestedness
```{r, nested}
#this step is slow & can be skipped w/o issues. load from csv but code is here.  takes 30 min 
# ne <- nestedcontribution(ind1)
# ne.low <- ne[[2]]
# ne.top <- ne[[1]]
# ne.low$uniID <- row.names(ne.low)
# write.csv(ne.low, "data/Output/nelow.csv")
# write.csv(ne.top, "data/Output/netop.csv")
ne.low <- read.csv("data/Output/nelow.csv")
ne.low <- select(ne.low, -X)
all <- left_join(all, ne.low, by = "uniID")
```

## Unipartitite modularity
```{r, unipartite modularity}
one1 <- as.one.mode(ind1, fill = 0, project = "lower", weighted = TRUE)
mods <- netcarto(one1)
n1data <- mods[[1]]
n1data <- rename(n1data, uniID = name)
all <- left_join(all, n1data, by = "uniID")
all$module <- as.factor(all$module)
```

These sections take a long time to run. Therefore, the output is stored in .csv but the code is commented out here. 

Individual-based network
```{r}
#make 1000 random networks, project to one-mode, compute modularity
#null.mod <- permatfull(ind1, fixedmar = "both", times = 1000)
#null.mod <- null.mod$perm
#null.one <- map(null.mod, as.one.mode, fill = 0, project = "lower", weighted = TRUE)
#null.module <- map(null.one, netcarto)

#t <- list()  
#for (i in 1:1000){
#    ind <- null.module[[i]][2]
#   t <- c(t, ind)
#  } 
#t <- unlist(t, use.names=FALSE)
#t <- as.data.frame(t)
#write.csv(t, "Data/Randomization_Outputs/randommoduleoutput_unipartite.csv")
t <- read.csv("Data/Randomization_Outputs/randommoduleoutput_unipartite.csv")
mods[[2]]
net.zscore(mods[[2]], t$t)

mean(t$t)

#print(null.module[[3]][2])

```


# EDA

```{r}
labels = c("Acamptopappus sphaerocephalus", "Eriogonum fasciculatum", "Ericameria cooperi", "Ericameria linearifolia", "Larrea tridentata", "Scutellaria mexicana", "Salvia dorri", "Echinocereus engelmannii", "Opuntia basilaris", "Cylindropuntia echinocarpa")

ggplot(data, aes(N.flowers, Quantity)) + geom_point(aes(color = Species)) + geom_smooth(method = lm, se = FALSE, color = "black") + scale_color_discrete("", labels = labels) + ylab("Visitation Rate") + xlab("Floral display size")

ggplot(data, aes(N.flowers, Height)) + geom_point(aes(color = Species)) + geom_smooth(method = lm, se = FALSE, color = "black") + scale_color_discrete("", labels = labels) + xlab("Floral display size")


ggplot(data, aes(shrub.density, Quantity)) + geom_point(aes(color = Species)) + geom_smooth(method = lm, se = FALSE, color = "black") + scale_color_discrete("", labels = labels) + ylab("Visitation rate") + xlab("Neighbourhood shrub density")

pl <- select(all, Species, shrub.density, dg1, st.con, st.het)
pl <- gather(pl,type, prop, 4:5)

ggplot(pl, aes(dg1, prop, color = type)) + geom_point()  +xlab("Degree Centrality") + ylab("Proportion of Population")

ggplot(pl, aes(shrub.density, prop, color = type)) + geom_point() + geom_smooth(method = lm) +xlab("Shrub Density") + ylab("Proportion of Population")

c <- select(all, 3:6, Quantity)
c <- rename(c, closeness = cls1, eigancentrality = V2, betweenness = bt1, degree = dg1, visitation.rate = Quantity)
M <- cor(c)
corrplot(M, method = "number") # Display the correlation coefficient
```

# Modelling


## Visitation rates
```{r, visitation rates}
m1 <- MASS::glm.nb(Quantity ~density + N.flowers + imp.den + Species, data = data)       
m1p <- glm(Quantity ~density + N.flowers + imp.den + Species, family = "poisson", data = data)    
check_overdispersion(m1p)
AIC(m1, m1p)
#negative binomial #2 is the best

m1 <- MASS::glm.nb(Quantity ~density * N.flowers + day + Species, data = data)
m2 <- MASS::glm.nb(Quantity ~ density + N.flowers + day + Species,  data = data)       
m3 <- MASS::glm.nb(Quantity ~ density + N.flowers * day + Species, data = data) 
m4 <-MASS::glm.nb(Quantity ~shrub.density * N.flowers + day + Species, data = data)
m5 <- MASS::glm.nb(Quantity ~ shrub.density + N.flowers + day + Species,data = data)    
m6 <- MASS::glm.nb(Quantity ~ shrub.density + N.flowers * day + Species,  data = data)

m6.2 <- MASS::glm.nb(Quantity ~ shrub.density + Height+day + N.flowers * day + Species,  data = data)
summary(m6.2)
check_collinearity(m6.2)
#including height increases colinearity

m6.3 <- MASS::glm.nb(Quantity ~ shrub.density + day + N.flowers * day + Species,  data = data)
AIC(m6.2, m6.3)

#including height increases colinearity without improving fit

m7 <- MASS::glm.nb(Quantity ~ cactus.density + N.flowers * day + Species, data = data)
m8 <- MASS::glm.nb(Quantity ~ con.density + N.flowers * day+ Species, data = data)

m9 <- MASS::glm.nb(Quantity ~ shrub.density + N.flowers * day + Species, data = data)
m10 <- MASS::glm.nb(Quantity ~ N.flowers * day + Species,  data = data)
m11 <- MASS::glm.nb(Quantity ~ density + N.flowers * day + Species,  data = data)

#m9.imp <- MASS::glm.nb(Quantity ~ shrub.density + N.flowers * imp.den + Species, data = data)
#AIC(m9.imp)

knitr::kable(anova(m10, m9, m11, test = "Chisq"))

anova(m9, m11)
anova(m10, m11)

#adding shrub density significantly improves model fits, but adding density does not.

aic.visits <- AIC(m1, m2, m3, m4, m5, m6, m7, m8, m10, m11)
knitr::kable(AIC(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11))

#anova(m6, mnull)
library(tab)
summary(m6)
tabglm(m6)
knitr::kable(car::Anova(m6, type = 3))
check_collinearity(m6)

#outputting "data" file to .csv for publication
```
## Centrality - degree

```{r, centrality measures}
#degree centrality

#choosing betweene error families
ggplot(all, aes(dg1)) + geom_density()
m2 <- MASS::glm.nb(dg1 ~ N.flowers+ Quantity + shrub.density + day + Species, data = all)
m3 <- glm(dg1 ~ N.flowers+ Quantity + shrub.density + day + Species, family = "poisson", data = all)
check_overdispersion(m3)
AIC(m2, m3)
#nbinom2

#check if interaction should be included
m7 <- MASS::glm.nb(dg1 ~ Quantity+ shrub.density + day  * N.flowers + Species, data = all)
AIC(m2, m7)


#mnull <- glmmTMB(dg1 ~  (1|Species), family = "nbinom2", data = all)



#model without interaction is best
summary(m2)
knitr::kable(car::Anova(m2, type = 2))
check_collinearity(m2)

```

## Betweenness
```{r, betweenness}
#betweeness
ggplot(all, aes(bt1)) + geom_density()

b2 <-glm(btbin ~ shrub.density + Quantity + day + N.flowers + Species, family = "binomial", data = all)


summary(b2)
car::Anova(b2, type = 2)


#bnull <- glmmTMB(btbin ~ 1 + (1|Species), family = "binomial", data = all)
#anova(b2, bnull)

summary(b2)
knitr::kable(car::Anova(b2, type = 2))
check_collinearity(b2)


#gaussian part


b4 <- glm(log(bt1) ~ Quantity + shrub.density + day + N.flowers + Species, family = "gaussian", data = bt)
shapiro.test(resid(b4))

#b4null <- glmmTMB(log(bt1) ~ (1|Species), family = "gaussian", data = bt)
#anova(b4, b4null)
check_collinearity(b4)

summary(b4)
knitr::kable(car::Anova(b4, type = 2))
```

## Eigancentrality

```{r, eigancentrality}
ggplot(all, aes(sqrt(V2))) + geom_density()


v2 <- glm(sqrt(V2) ~ Quantity+ shrub.density + N.flowers + day +Species, family = "gaussian", data = all)

shapiro.test(resid(v2))
hist(resid(v2))
#histogram looks fine

check_collinearity(v2)

summary(v2)
knitr::kable(car::Anova(v2, type = 2))

ggplot(all, aes(Species, V2)) + geom_boxplot() + ylab("Eigancentrality")

```

#maybe just use the number of sampled plants as an offset??
#conspecifics
```{r}
#all <- rename(all, cons = cons.x, hets = hets.x, n = n.x)
all <- mutate(all, uncon = n - cons)
y <- cbind(all$cons, all$uncon)

m4 <- glm(y ~ shrub.density+ dg1 + N.flowers + day +Species, family = "binomial"(link = "logit"), data = all)
summary(m4)
#interact_plot(m4, dg1, Quantity)


#check_overdispersion(m4)
#performance use to work on binomial too, residual deviance still suggests over though
#overdispersed


cor.test(all$dg1, all$Quantity)
cor.test(all$bt1, all$dg1)


m4.2 <- glm(y ~ shrub.density+ dg1+ N.flowers + day + Species + Quantity, family = "quasibinomial"(link = "logit"), data = all)
summary(m4.2)

AIC(m4, m4.2)

knitr::kable(car::Anova(m4.2, type = 2))



#check_collinearity(m4)
#check_overdispersion(m4)

summary(m4)
m4 <- glm(y ~ shrub.density+ dg1 + N.flowers + day + Species, family = "quasibinomial"(link = "logit"), data = all)
summary(m4)
knitr::kable(car::Anova(m4, type = 2))
car::vif(m4)





cor.test(all$shrub.density, all$dg1)

#heterospecific access
all <- mutate(all, unhet = hetn - hets)
z <- cbind(all$hets, all$unhet)

m1 <- glm(z ~ day + shrub.density+ dg1+ N.flowers+ Species, family = "binomial"(link = "logit"), data = all)
summary(m1)
#check_overdispersion(m1)
#also overdisperse


m5.2 <- glm(z ~ dg1 + shrub.density + N.flowers + day +Species, family = "quasibinomial"(link = "logit"), data = all)
summary(m5.2)
knitr::kable(car::Anova(m5.2, type = 2))

cor.test(all$dg1, all$Quantity)
```

## Effective partners
```{r}


ggplot(all, aes(effective.partners)) + geom_density()

m1 <- glm(effective.partners ~ Quantity + shrub.density + N.flowers + day +Species, family = "gaussian", data = all)
hist(resid(m1))

m2 <- glm(effective.partners ~ Quantity + shrub.density + N.flowers + day + Species, family = Gamma(link = "log"), data = all)


AIC(m1,m2)

shapiro.test(all$effective.partners)

summary(m2)
knitr::kable(car::Anova(m2, type = 2))
check_collinearity(m2)

ggplot(all, aes(Species, effective.partners)) + geom_boxplot()

```

## Nestedness

```{r, nestedness}
ggplot(all, aes(nestedcontribution)) + geom_density()
shapiro.test(all$nestedcontribution)

n1 <- glm(nestedcontribution ~ N.flowers+day  + Quantity  + shrub.density + 
            Species, family = "gaussian", data = all)
shapiro.test(resid(n1))

car::vif(n1)


summary(n1)
knitr::kable(car::Anova(n1, type = 2))

```

#Modules and modularity modelling

```{r, module}
library(nnet)

m1 <- multinom(module ~ Species + shrub.density  + Quantity+ N.flowers + day, data = all)
summary(m1)
options(scipen=999)
knitr::kable(car::Anova(m1, type = 2))

  
```

# Network comparisons


The random network parts take a really long time to run, therefore are output as csv and read back in. Code is commented out. 

These are all bipartite networks
```{r}

#calculate network level indices for the bipartite networks. 

#make a species network
sp <- net(visits, Species, ID)
write.csv(sp, "Data/species_network.csv")
n <- networklevel(sp)
n <- as.data.frame(n)

#output networks repo
write.csv(ind1, "Data/individal_network.csv")


#use existing individual network
#i <- as.data.frame(networklevel(ind1))
#write.csv(i, "data/Output/ind_network_indices.csv")
i <- read.csv("data/Output/ind_network_indices.csv")
sp.m <- computeModules(sp)

i.m <- computeModules(ind1)

mod <- i.m@moduleWeb

#run the random modules function on the species network
#sp.ran.mod <- ranModules(sp)
#write.csv(sp.ran.mod, "data/Randomization_outputs/randommodule_sp_bi.csv")

sp.ran.mod <- read.csv("data/Randomization_outputs/randommodule_sp_bi.csv")
mean(sp.ran.mod$`X..`)
net.zscore(sp.m@likelihood, sp.ran.mod$`X..`)

#run the random modules function on the individual network, takes ~72 hours
#ind.ran.mod <- ranModules(ind1)
#write.csv(ind.ran.mod, "Data/Randomization_outputs/randommoduleoutput_bipartite.csv")

ind.ran.mod <- read.csv("Data/Randomization_outputs/randommoduleoutput_bipartite.csv")
ind.ran.mod$t <- ind.ran.mod$X..i..
net.zscore(i.m@likelihood, ind.ran.mod$t)
mean(ind.ran.mod$t)
max(ind.ran.mod$t)

#individual networks

ind.WC <- ranindices(ind1, "weighted connectance")
ind.WNODF <-ranindices(ind1, "weighted NODF")
ind.H2 <- ranindices(ind1, "H2")

net.zscore(i[10,2], ind.WNODF$`weighted NODF`)
mean(ind.WNODF$`weighted NODF`)
max(ind.WNODF$`weighted NODF`)
min(ind.WNODF$`weighted NODF`)

net.zscore(i[14,2], ind.WC$`weighted connectance`)
mean(ind.WC$`weighted connectance`)
max(ind.WC$`weighted connectance`)
min(ind.WC$`weighted connectance`)

net.zscore(i[19,2], ind.H2$H2)
mean(ind.H2$H2)
max(ind.H2$H2)

#species networks

sp.WNODF <- ranindices(sp, "weighted NODF")
net.zscore(n[10,], sp.WNODF$`weighted NODF`)
mean(sp.WNODF$`weighted NODF`)
max(sp.WNODF$`weighted NODF`)

sp.WC <- ranindices(sp, "weighted connectance")
n[14,]
net.zscore(n[14,], sp.WC$`weighted connectance`)
mean(sp.WC$`weighted connectance`)
max(sp.WC$`weighted connectance`)



sp.H2 <- ranindices(sp, "H2")
n[19,]
net.zscore(n[19,], sp.H2$H2)
mean(sp.H2$H2)
```






```{r}
#violindles
ggplot(filter(all, module != "NA"), aes(module, Quantity)) + geom_violin() + stat_summary(fun.y=mean, geom="point", shape=23, size=2) + geom_jitter(aes(color = Species, shape = Species), position=position_jitter(0.2)) + ylab("Visitation Rate") + xlab("Module") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + scale_shape_manual(values=c(3, 16, 17, 3, 16, 17, 3, 16, 17), labels = labels) +scale_color_discrete(name = "Species", labels = labels)
 
labels = c("Acamptopappus sphaerocephalus", "Eriogonum fasciculatum", "Ericameria cooperi", "Echinocereus engelmannii", "Larrea tridentata", "Opuntia basilaris", "Cylindropuntia echinocarpa", "Salvia dorri", "Scutellaria mexicana")

ggplot(all, aes(module, N.flowers)) + geom_boxplot()
ggplot(all, aes(module, shrub.density)) + geom_boxplot()


#centrality species comparisons
#make a smaller dataframe of means and se for figure 1
library(ggthemes)
se <- function(x) {sd(x)/sqrt(length(x))} ## SE
central.means <- all %>% group_by(Species) %>% summarise(dg = mean(dg1), visits = mean(Quantity), eig = mean(V2), bt = mean(bt1)) %>% gather(var, mean, 2:5)
central.se <- all %>% group_by(Species) %>% summarise(dg = se(dg1), visits = se(Quantity), eig = se(V2), bt = se(bt1)) %>% gather(var, se, 2:5)
cent <- cbind(central.means, central.se)
cent <- cent[,c(1,2,3,6)]
cent$var <- factor(cent$var, levels = c("visits", "dg", "eig", "bt", labels = c("Visitation Rates", "Degree centrality", "Eigenvector Centrality", "Betweenness")))

ggplot(cent, aes(Species, mean)) + geom_point(stat = "identity", aes(fill = Species)) +  geom_errorbar(aes(Species, ymin = mean - se, ymax = mean + se)) + theme_classic() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + facet_wrap(.~var, scales = "free")  


visit_plot <- filter(cent, var == "visits")
dg_plot <- filter(cent, var == "dg")
eig_plot <- filter(cent, var == "eig")
bt_plot <- filter(cent, var == "bt")

a <- ggplot(visit_plot, aes(Species, mean)) + geom_point() +  geom_errorbar(aes(Species, ymin = mean - se, ymax = mean + se)) + theme_classic() + ylab("Mean Visitation Rate") + xlab("") + theme(axis.text.x = element_blank(),panel.border = element_rect(colour = "black", fill=NA, size=1), aspect.ratio = 1) + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))


b <- ggplot(dg_plot, aes(Species, mean)) + geom_point() +  geom_errorbar(aes(Species, ymin = mean - se, ymax = mean + se)) + theme_classic() + ylab("Mean Degree Centrality") + xlab("") + theme(axis.text.x = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), aspect.ratio = 1) + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))

c <- ggplot(eig_plot, aes(Species, mean, fill = Species)) + geom_point() +  geom_errorbar(aes(Species, ymin = mean - se, ymax = mean + se)) + theme_classic() + ylab("Mean Eigenvector Centrality") + scale_x_discrete(labels = labels) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1), axis.text.x = element_text(angle = 90, hjust = 0.95, vjust = .1), legend.position = "none", aspect.ratio = 1) + xlab("") + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))

d <- ggplot(bt_plot, aes(Species, mean, fill = Species)) + geom_point() +  geom_errorbar(aes(Species, ymin = mean - se, ymax = mean + se)) + theme_classic() + ylab("Mean Betweenness Centrality") + scale_x_discrete(labels = labels) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1), axis.text.x = element_text(angle = 90, hjust = 0.95, vjust = .1), legend.position = "none") + xlab("") + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))


library(gridExtra)

fig1 <- grid.arrange(a, b, c, d, ncol = 2, heights = c(1, 1.4), widths = c(1, 1.4))

#Figure 2



e <- ggplot(pl, aes(dg1, prop, color = type)) + geom_point()  +xlab("Degree Centrality")+ geom_smooth(method = lm) + ylab("Proportion of Population") + scale_color_discrete(name = "", labels = c("Conspecific", "Heterospecific")) + theme_classic() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + theme(legend.position = "none", aspect.ratio = 1)

f <- ggplot(pl, aes(shrub.density, prop, color = type)) + geom_point() + geom_smooth(method = lm) +xlab("Shrub Density") + ylab("Proportion of Population") + scale_color_discrete(name = "", labels = c("Conspecific", "Heterospecific")) + theme_classic() + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), legend.position = "bottom", aspect.ratio = 1) 
e



a + b + plot_layout(ncol = 2)
c + d + plot_layout(ncol = 2)
e + f + plot_layout(ncol = 1)



```
